Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-16 semantic-nd/article.tex
small changes (including some subtitles)

Describing the distribution function in terms of graphs allows to use algorithms
such as the Sum-Product~\citep{kschischang2001factor} to efficiently calculate
marginals on any given subset $x_m$ of variables by exploiting conditional
independence between variables.

@@

\subsection{Suitable functions for implementing a Static Threshold}
%%% Results 1
% Show the threshold ratio is an optimal detector (if perfect information was available)
% Show that the thresholds are suitable functions for implementing a static threshold.
As first tryout, the performance of the novelty thresholds was plotted for a set
of 1000 samples taken out from the whole distribution (\autoref{fig:synthetic-roc}).
Those samples contain different number of sensed properties for each room, miming
the dynamic properties expected to see when implemented on a robot.

@@

%%% Results 2
% Measure performance of the thresholds as more information becomes available.
\subsection{Performance impact as more information becomes available}
In order to measure the performance impact as more semantic information becomes
available ROC curves were plotted for samples grouped by the number of sensed
semantic properties.

@@

The uniform threshold shows a very poor performance specially on small size samples
where its performs almost no better than random.
It performance increases as the size of sensed features increases but nonetheless
its always very small when compared to how optimal a threshold could be.
This shows that at least under semantic distributions as the one modelled with the
synthetic data assuming an uniform unconditional distribution is a very bad choice.

>>>>

Describing the distribution function in terms of graphs allows to use algorithms
such as the Sum-Product~\citep{kschischang2001factor} to efficiently calculate
marginals on any given subset of variables by exploiting conditional
independence between variables.

@@

\subsection{Probability ratio comparison}
%%% Results 1
% Show the threshold ratio is an optimal detector (if perfect information was available)
% Show that the thresholds are suitable functions for implementing a static threshold.
As first tryout, the performance of the novelty thresholds was plotted for a set
of 1000 samples taken out from the whole distribution (\autoref{fig:synthetic-roc}).
Those samples contain different number of sensed properties for each room, miming
the dynamic properties expected to see when implemented on a robot.

@@

%%% Results 2
% Measure performance of the thresholds as more information becomes available.
\subsection{Performance changes with amount of available information}
In order to measure the performance impact as more semantic information becomes
available ROC curves were plotted for samples grouped by the number of sensed
semantic features.

@@

The uniform threshold shows a very poor performance specially on small size samples
where its performs almost no better than random.
It performance increases as the size of sensed features increases but nonetheless
its always very small when compared to how optimal a threshold could be.
This shows that at least under semantic distributions as the one modelled with the
synthetic data assuming an uniform unconditional distribution leads to poor results.
